\label{sec:issues}
These issues have been noted earlier in email and Basecamp, and
are provided here only for the sake of completeness.
\begin{itemize}
\item In app/files/views.py, for every login\_required view, the
  \@login\_required decorator has been removed, the view function
  name changed to view\_reg, and a login\_required version is
  retained with the original view name.  The view\_reg functions
  do not have configured URLs, and are hence not accessible. The
  only exception is login\_reg, access to which is blocked from
  non-registered IP addresses by the middleware.
\item Users after logging in were supposed to be redirected to
  '/home/'. This URL does not exist, so the redirection has been
  made to '/'
\item Users from registered IPs looking at non-admin views cannot
  be authenticated (there is no user/password information). Hence
  the views should not have specific information shown for
  authenticated users.
\item A user who has been authenticated from a registered
  (unregistered) IP, and switches to an unregistered (registered)
  IP is not required to authenticate again, and retains all
  earlier privileges.
\item The login template is now set in the middleware, using the
  values in settings\_local.py. This means that any values passed
  with 'template\_name' to the login view in urls.py will be
  overriden.
\item Currently, in urls.py
  \begin{Verbatim}
    (r'^admin/(.#)', include(admin.site.urls)),
  \end{Verbatim}
  is preferred for the admin. site configuration, instead of,
  \begin{Verbatim}
    (r'^admin/(.#)', admin.site.root),
  \end{Verbatim}
  Please see \url{http://docs.djangoproject.com/en/dev/ref/contrib/admin/#hooking-adminsite-instances-into-your-urlconf}. With the old style declaration, I am
  forced to use
  \begin{Verbatim}
    reverse(admin.site.root, args=['']) 
  \end{Verbatim}
  to get the root of the admin. site URL. admin.site.root is deprecated
  and will disappear in Django 1.3. Now, the admin. uses named URLs, so
  that the usage should be
  \begin{Verbatim}
    reverse('admin\_index', args=[''])
  \end{Verbatim}
  However, this will work only with the above changes to urls.py.
\item app.files.eps is not protected by \@login\_required. I am not sure why
  this is the case, and have left it alone.
\end{itemize}